Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Rather than trying to trace cultural features at large, we intend to focus on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person" [@OECD2009].

@@

Another interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was slightly different. They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes. We believe there is a more widely spread systematic effect of educational features. The cross-cultural perspective on teaching and learning proposed by Watkins [@Watkins2010] shall help us compare countries. Cheng and Wong’s study about school effectiveness in East Asia [@Cheng2006] will also help.

>>>>

Rather than trying to trace cultural features at large, we intend to focus on one key cultural institution, that is the education system. Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996]. Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].

@@

Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009]

Variable | France | UK
-------------|---------------|---------
Sense of belonging (PISA 2012) | 47% | 79%

Another interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was slightly different. They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes. We believe there is a more widely spread systematic effect of educational features.

The cross-cultural perspective on teaching and learning proposed by Watkins [@Watkins2010] shall help us compare countries.

Cheng and Wong’s study about school effectiveness in East Asia [@Cheng2006] will also help.
